Compilation With Program Synthesis

### 2023-08-22 new-paper/paper.tex
Bring more things over
SuSLik extension section
related work; more consistency in notation
Describe layouts
a small fix

\documentclass[acmsmall]{acmart}
\usepackage{graphicx}
\usepackage{proof}
\usepackage{stmaryrd}
\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{syntax}
\usepackage{listings}
\lstset{basicstyle=\ttfamily, mathescape=true, literate={~} {$\sim$}{1}}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Synthetic Separation Logic (SSL) is a specification language used by the \SuSLik{} program synthesis tool.
  \SuSLik{} will take a Hoare-style specification expressed in SSL and synthesize a program that satisfies this
  specification in a C-like language. However, these specifications are very low-level and SSL does not allow for much abstraction. In this paper,
  we explore a connection between SSL specifications and functional programming. We give a first-order functional
  programming language, \Pika, which has both a standard semantics and a translation into SSL that respects the standard semantics.

@@

\input{introduction}
\input{overview}
\input{syntax}
\input{layouts}
\input{semantics}
\input{limitations}
\input{synth}
\input{examples}
\input{future-work}
\input{conclusion}

>>>>

\documentclass[acmsmall]{acmart}
\usepackage{graphicx}
\usepackage{proof}
\usepackage{stmaryrd}
\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{syntax}
\usepackage{listings}
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{mathpartir}
\lstset{basicstyle=\ttfamily, mathescape=true, literate={~} {$\sim$}{1}}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Synthetic Separation Logic (SSL) is a specification language used by the \SuSLik{} program synthesis tool.
  \SuSLik{} will take a Hoare-style specification expressed in SSL and synthesize a program that satisfies this
  specification in a C-like language. However, these specifications are very low-level and SSL does not allow for much abstraction. In this paper,
  we explore a connection between SSL specifications and functional programming. We give a functional
  programming language, \Pika, which has both a standard semantics and a translation into SSL that respects the standard semantics.

@@

\input{selected-rules}

\input{introduction}
\input{overview}
% \input{syntax}
\input{semantics}
\input{suslik-extensions}
\input{limitations}
\input{synth}
\input{examples}
\input{related-work}
\input{future-work}
\input{conclusion}

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}
